Title

### 2024-06-22 paper/main.tex
Updates

The idea behind using the measure of association for modifying DAGs is inspired
by modification indices in SEM. For any given model and a dataset, we can use
the condtiional measure of association to compute the amount of correlation in
the data that is still not explained by the model. Based on this, we can
compute how much improvement in the explanation would happen if we were to add
an edge between variables. This can then be ranked using the maximum
improvement. Give some examples here.

>>>>

The idea behind using the measure of association for modifying DAGs is inspired
by modification indices in SEM.
